Spin canonical divisors of log stacky curves

### 2015-06-28 stacky_write_up/spin_cring.tex
reorder g0 slightly

@@

Furthermore, we can directly see that the relations are given
in degrees $10$ and $14$. In particular, we have relations
\begin{align*}
	&a_1 x_{5, 1}^2 + a_2 x_{3, 1} x_{7, 1} + a_3 x_{3, 1} x_{7, 2} = 0 &\text{ in degree $10$} \\
	&b_1 x_{7, 1}^2 + b_2 x_{3, 1}^3 x_{5, 1} + b_3 x_{7, 1} x_{7, 2} + b_4 x_{7, 2}^2 = 0  &\text{ in degree $14$}
\end{align*}

@@

Therefore, the canonical ring $R'$ has presentation $R' =
k[x_{7, 1}, x_{7, 2}, x_{5, 1}, x_{3, 1}] / I$ with
initial ideal $in_\prec(I)$ generated by quadratics under grlex
with $x_{7,1} \prec x_{7,2} \prec x_{5,1} \prec x_{3,1}$
%These quadratics must also determine minimal generators for $I$ by
%Lemma ~\ref{lem:minimal_quadratic}.
Thus, $R'$ is generated up to
degree $e = 7$ with relations up to degree $2e = 14$, as desired.s

%We can also see that $e_i > \deg z$ for any generator $z$ of $R'$
%since $e_i = 9 > e$ for all $i \in J$.

Admissibility is the remaining condition to check. By relabelling the variables if necessary, we can assume
that $x_{7, 1}$ corresponds to the generator with maximal pole order
at $P_2$ and $x_{7, 2}$ correspond to the generator with maximal
pole order at $P_3$. \todo{There is actually a small problem here, which needs to be fixed earlier. I think in order to satisfy admissibility, you will actually have to choose $x_{7,i}$ from the beginning to satisfy these constraints, as this will not generically be true. Just make sure to put these constraints on the poles when you define $x_{7,i}$} Use the presentation given
above with $y _{2, e_2'} := x_{7, 1}$ and $y_{3, e_3'} :=  x_{7, 2}$.
We see that it immediately satisfies (Ad-i) of Definition
~\ref{defn:admissible}. We may also choose pole orders of the generators
such that $y_{i, e_i'}$ is the only generator lying on the line
$-ord_{P_i}(z) = \deg z \frac{3d}{7}$ in the $(\deg z, -ord_{P_i}(z))$
 lattice and with the other generators lying below the line as seen
in Figure ~\ref{fig:377} (e.g. the pole orders $(-ord_{P_1}(z)$,
$-ord_{P_2}(z)$, $-ord_{P_3}(z))$ may be chosen to be $(1, 1, 1)$,
$(1, 2, 2)$, $(2, 3, 2)$, and $(2, 2, 3)$ for $z = x_{3, 1}, x_{5, 1},
x_{7, 1}, x_{7, 2}$ respectively).

Also note that $e_j' + 2d = 7 + 2d \nmid 2 = e_i - e_j'$ for all
$i, j \in J_2 = \{2, 3\}$ such that $j \neq i$ and for all $d \geq
0$. Thus, $s_{\sigma_2, J_2}(i, d) = \emptyset$ for each $i \in J$.
Furthermore, $\deg \lfloor e_i \halfcan \rfloor = \deg \lfloor 9
\halfcan \rfloor = 2 \lfloor \frac{4 * 9}{9} \rfloor + \lfloor
\frac{9}{3} \rfloor - 9 = 2$, so (Ad-iii) is satisfied and
$\sigma_2, J_2$ is admissible.
\end{example}

>>>>

Now, we check admissibility. By relabelling the
variables if necessary, we can assume that $x_{7, 1}$ corresponds
to the generator with maximal pole order at $P_2$ and $x_{7, 2}$
correspond to the generator with maximal pole order at $P_3$. Use
the presentation given above with $y _{2, e_2'} := x_{7, 1}$ and
$y_{3, e_3'} :=  x_{7, 2}$. We see that it immediately satisfies
(Ad-i) of Definition ~\ref{defn:admissible}. We may also choose
pole orders of the generators such that $y_{i, e_i'}$ is the only
generator lying on the line $-ord_{P_i}(z) = \deg z \frac{3d}{7}$
in the $(\deg z, -ord_{P_i}(z))$  lattice and with the other
generators lying below the line as seen in Figure ~\ref{fig:377}
(e.g. the pole orders $(-ord_{P_1}(z)$, $-ord_{P_2}(z)$, $-ord_{P_3}
(z))$ may be chosen to be $(1, 1, 1)$, $(1, 2, 2)$, $(2, 3, 2)$,
and $(2, 2, 3)$ for $z = x_{3, 1}, x_{5, 1}, x_{7, 1}, x_{7, 2}$
respectively).

Also note that $e_j' + 2d = 7 + 2d \nmid 2 = e_i - e_j'$ for all
$i, j \in J_2 = \{2, 3\}$ such that $j \neq i$ and for all $d \geq
0$. Thus, $s_{\sigma_2, J_2}(i, d) = \emptyset$ for each $i \in J$.
Furthermore, $\deg \lfloor e_i \halfcan \rfloor = \deg \lfloor 9
\halfcan \rfloor = 2 \lfloor \frac{4 * 9}{9} \rfloor + \lfloor
\frac{9}{3} \rfloor - 9 = 2$, so (Ad-iii) is satisfied and
$\sigma_2, J_2$ is admissible.

@@

We can directly see that the relations are given in degrees $10$
and $14$. In particular, we have relations
\begin{align*}
	&a_1 x_{5, 1}^2 + a_2 x_{3, 1} x_{7, 1} + a_3 x_{3, 1} x_{7, 2} = 
0 &\text{ in degree $10$} \\
	&b_1 x_{7, 1}^2 + b_2 x_{3, 1}^3 x_{5, 1} + b_3 x_{7, 1} x_{7, 2} 
+ b_4 x_{7, 2}^2 = 0  &\text{ in degree $14$}
\end{align*}

@@

Therefore, the canonical ring $R'$ has presentation $R' =
k[x_{7, 1}, x_{7, 2}, x_{5, 1}, x_{3, 1}] / I$ with
initial ideal $in_\prec(I)$ generated by quadratics under grlex
with $x_{7,1} \prec x_{7,2} \prec x_{5,1} \prec x_{3,1}$.
%These quadratics must also determine minimal generators for $I$ by
%Lemma ~\ref{lem:minimal_quadratic}.
Thus, $R'$ is generated up to degree $e = 7$ with relations up to
degree $2e = 14$, as desired.

%We can also see that $e_i > \deg z$ for any generator $z$ of $R'$
%since $e_i = 9 > e$ for all $i \in J$.
\end{example}
